Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-02 longSC.tex
add reference and moving model to the comparison part

The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey. For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations support as well the view that $\eta/s$ of the QGP matter is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2015qia}. This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

\section{Theoretical models}
\label{sec:models}
%We have used various models in this article. The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.

@@

\section{Model Comparisons}
\label{sec:theory}
\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. This observation helps to understand better the fluctuations in initial energy density.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values. This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions. The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.

@@

The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), none of the calculations can describe the data and calculation with the default AMPT setting follows the trend of the data closest. The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

@@

>>>>

The temperature dependence of the $\eta/s$ has some generic features that most of the known fluids obey. For instance, one such general behavior is that the ratio typically reaches its minimum value close to the phase transition region~\cite{Lacey:2006bc}. 
It was shown, using kinetic theory and quantum mechanical considerations~\cite{PhysRevD.31.53}, that $\eta/s\sim0.1$ would be the correct order of magnitude for the lowest possible shear viscosity to entropy ratio value found in nature. Later it was demonstrated that an exact lower bound $(\eta/s)_{\rm min}=1/4\pi\approx0.08$ can be calculated using the AdS/CFT correspondence~\cite{Kovtun:2004de}. Hydrodynamical simulations support as well the view that $\eta/s$ of the QGP matter is close to that limit~\cite{Gale:2012rq}. This may have important implications for other fundamental physics goals. It is argued that such a low value might imply that thermodynamic trajectories for the expanding matter would lie close to the quantum chromodynamics (QCD) critical end point, which is another subject of intensive experimental quest~\cite{Lacey:2006bc,Csernai:2006zz}.
%which in turn would gain better prospects to search of critical end point~\cite{PhysRevLett.98.092301}.

@@

The existing measurements provide an estimate of the average value of QGP's $\eta/s$, both at RHIC and LHC energies. What remains uncertain is how the $\eta/s$ of QGP depends on temperature ($T$)~\cite{Niemi:2011ix,Niemi:2015qia}. This study has been just initiated by the theorists in Ref.~\cite{Niemi:2015qia}, where the first (and only rather qualitative) possibilities where investigated (see Fig.~1 therein). The emerging picture is that the study of individual flow harmonics $v_n$ will unlikely reveal the details of $\eta/s(T)$ dependence.
It was demonstrated already in \cite{Niemi:2015qia} that different $\eta/s(T)$ parameterizations can lead to the same centrality dependence of individual flow harmonics. In Ref.~\cite{Niemi:2012aj} new flow observables were introduced which quantify the degree of correlation between two different harmonics $v_m$ and $v_n$. These new observables have potential to discriminate the contributions to anisotropic flow development from initial conditions and from the transport properties of the QGP~\cite{Niemi:2012aj}. Therefore their measurements would provide the experimental constrains of the theoretical predictions for individual stages of heavy-ion evolution independently. In addition, it turned out that correlations of different flow harmonics are sensitive to the temperature dependence of $\eta/s$~\cite{ALICE:2016kpq}, to which individual flow harmonics are weakly sensitive~\cite{Niemi:2015qia}.

@@

@@

\section{Model Comparisons}
\label{sec:theory}
\subsection{Theoretical models}
\label{sec:models}
%We have used various models in this article. The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.

\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. This observation helps to understand better the fluctuations in initial energy density.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values. This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions. The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.

@@

The SC($m$,$n$) calculated from AMPT simulations are compared to data in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), none of the calculations can describe the data and the calculation with the default AMPT setting follows the trend of the data closest. The same default calculation can describe the sign and magnitude of NSC(3,2) while the hydrodynamic calculations failed to describe the sign and magnitude of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot reproduce the data and the strength of the correlation is weaker than in data.
The third version based on the string melting configuration without the hadronic rescattering phase is also shown.
The hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

@@

We list here a few important findings from the model comparison:
\begin{itemize}
	\item A hierarchy NSC(5,3) $>$ NSC(4,2) $>$ NSC(5,2) holds for centrality ranges $>20\%$ within the errors and NSC(5,2) is smaller than NSC(5,3) while SC(5,2) is larger that SC(5,3). This hierarchy is well reproduced by hydrodynamic model calculations and AMPT model calculations.
	\item All the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of correlations.
	\item Among the calculations with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
	\item The sign of $v_3$ and $v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations while the default AMPT model can reproduce the sign.
	\item The default AMPT model can describe NSC quantitively.
	\item The hadronic rescattering in AMPT model makes the correlation strength (NSC) larger.
\end{itemize}
